The problem and promise of scale in multilayer animal social networks

### 2020-02-12 paper/manuscript.Rmd
add todo
edits nobs

We altered the social scale based on visual (short distance) and auditory (long
distance) sensory modalities of caribou<!-- TODO: REF?-->. Specifically, we
modified the spatial distance threshold required for group assignment using
`spatsoc` [@Robitaille_2019] (see above) and re-assigned groups at incremental
distances between 5 - 500 m. For example, at the finest social scale, only
individuals within 5 m of one another were considered in the same group, whereas
at the coarsest social scale, individuals within 500 m of one another were
considered in the same group.

@@

#### Number of observations
Studies of social network analysis vary in the number and frequency of
observations as well as the data collection technique used to generate networks
[@Davis_2018; @Webber_2019]. In addition to altering the temporal scale by
adjusting the time window, we investigated the influence of the number of
observations on resulting multilayer networks. We randomly selected 500
timesteps and iteratively included 25 additional observations, regenerating the
multilayer network and calculating associations of individuals. Subsequent
iterations included the previous set of observations to mimic observational
data. <!-- TODO: bah conclude / this sentence falls off a cliff -->

>>>>

We altered the social scale based on visual (short distance) and auditory (long
distance) sensory modalities of caribou<!-- TODO: REF? / see EVW comment-->. Specifically, we
modified the spatial distance threshold required for group assignment using
`spatsoc` [@Robitaille_2019] (see above) and re-assigned groups at incremental
distances between 5 - 500 m. For example, at the finest social scale, only
individuals within 5 m of one another were considered in the same group, whereas
at the coarsest social scale, individuals within 500 m of one another were
considered in the same group.

@@

#### Number of observations
Studies of social network analysis vary in the number and frequency of
observations as well as the data collection technique used to generate networks
[@Davis_2018; @Webber_2019]. For example, GPS data is commonly collected at a
fixed rate (eg every $x$ minutes or hours) continuously throughout the study
period. We investigated the influence of the number of observations on resulting
multilayer networks. We randomly selected 500 timesteps and iteratively included
25 additional observations, regenerating the multilayer network and calculating
associations of individuals. Subsequent iterations included the previous set of
observations to mimic collection of observational data. <!-- TODO: bah conclude
/ this sentence falls off a cliff -->
